Topological Equivariant Artist Model

### 2022-03-29 slides/main.tex
compiled arrows w/ q

\begin{frame}<presentation:1|handout:1>{$\dfuncc = (\dfunchc, \dfunctc)$}
    \begin{figure}
        \includegraphics[width=0.5\textwidth]{figures/math/dfunc.png}
    \end{figure}
    \begin{description}
        \item[Base Transformation:] {$\dfunchc: \opensetc^{\prime} \rightarrow \opensetc$ where $\opensetc, \opensetc^{\prime} \subseteq \dbasec$, \\
        $\dfuncpullc\dsectionc\restriction_{\opensetc}: \dsectionc \mapsto \dsectionc\restriction_{\opensetc} \circ \dfunchc$}

@@

\section{Construction}
\begin{frame}<presentation:1|handout:1>{Building an equivariant $\vartist$?}
    \note{Add box around figure & lable it artist}
    \begin{figure}
        \includegraphics[width=1\textwidth]{../paper/figures/path_of_q.png}
    \end{figure}
\end{frame}

\subsection{Measurement Specification $\vtotalc$}

@@

\begin{frame}<presentation:1|handout:1>
    \frametitle{Transformations in Data $\vchannelc: \dsectionc \mapsto \vsectionc$}
    %rewrite in gamma notation
    \begin{figure}
        \includegraphics[.35\textwidth]{figures/math/nu_table.png}
    \end{figure}
    Given $\dsectionc(\dbasepointc) = \dsectionc(\dfunchc(\dbasepointc^{\prime}))$ and  $\vsectionc(\dbasepointc) = \vsectionc(\dfunchc(\dbasepointc^{\prime}))$
    \begin{description}
        \item[equivariance] $\dfunctc_{\vtotalc}(\vchannelc_{\opensetc}(\dsectionc))
        = \vchannelc_{\opensetc}(\dfunctc_{\dtotalc}(\dsectionc))$, $\vchannelc_{\opensetc} = {\vchannelc^{\prime}}_{\opensetc^{\prime}}$
        \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
    \end{description}
\end{frame}

@@

\subsection{Combining Components into Visualizations}
\begin{frame}<presentation:1|handout:1>{Assembly $\vmarkc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
            \arrow[rrrr, "\vmarkc", color=artist] 
            \arrow[ddd, "\dfunctc_{\vtotalc} \circ \dfuncpullc_{\vtotalc}"', color=action] 
            \& \& \& \& 
            \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[ddd, "\dfunctc_{\gtotalc} \circ \dfuncpullc_{\gtotalc}", dotted, color=action]  \\
            \& 
            \opensetc 
             \&  \& 
            \opensetgc 
            \arrow[ll, "\vindexc"', color=functor]   \& \\
            \& 
            \opensetc^{\prime} 
            \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
            \&  \& 
            \opensetgc^{\prime} 
            \arrow[ll, "\vindexc"', color=functor] 
            \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
            \& \\
            \cgamma{\opensetc^{\prime}}{\vtotalc^{\prime}\restriction_{\opensetc^{\prime}}}
            \arrow[rrrr, "\vmarkc^{\prime}", color=artist] 
            \& \&  \& \& 
            \imartist{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
            \end{tikzcd}
        \end{equation*}
    \begin{alertblock}{equivariance}
       \begin{equation*}
        \vmarkc^{\prime}(\dfunctc_{\vtotalc}(\vsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vmarkc(\vsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
       \end{equation*}
    \end{alertblock}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.15]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Implementation Choices: $\vartistc_{\dbasec} = \vartistc_{\gbasec}$}
    \begin{figure}
        \includegraphics[scale=.5]{figures/math/implement_paths).png}
    \end{figure}
\end{frame}

\begin{frame}{Combining Qs}
    The codomain of all $\vmarkc$ targeting the same output space is the bundle $\gtotalc$ and $Hom(\gbasec_1, \gtotalc) + Hom(\gbasec_2, \gtotalc) = Hom(\gbasec_1 + \gbasec_2, \gtotalc)$; therefore 
    $\sqcup \vmarkc_i(\cgamma{\opensetc_i}{\dtotalc_i\restriction_{\opensetc_i}}) = \cgamma{\sqcup \opensetgc_i}{\gtotalc\restriction_{\sqcup\opensetgc_i}}$
    \begin{figure}
        \includegraphics[scale=.25]{figures/math/qcom.png}
    \end{figure}
\end{frame}

\begin{frame}{Compatible Qs}
    \includegraphics[scale=.5]{figures/math/compatiblw_q.png}
\end{frame}
\end{document}

>>>>

\begin{frame}<presentation:1|handout:1>{$\dfuncc = (\dfunchc, \dfunctc)$}

    \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&, column sep=.3em]
                \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
                \arrow[rr, "\dfuncpullc", color=dfuncc] \&  \& 
                \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \&  \& 
                \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}}
                \arrow[rr, "\dfunctc", color=dfuncc] 
                \&  \& 
                \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \\
                \& \& \& \&  \&  \&  \\
                \opensetc 
                \arrow[uu, maps to, color=sheaf] \&  \& 
                \opensetc^{\prime} 
                \arrow[uu, maps to, color=sheaf] 
                \arrow[ll, "\dfunchc"', color=dfuncc] 
                \& \& \& \&                                                                       
            \end{tikzcd}
    \end{equation*}
    \begin{description}
        \item[Base Transformation:] {$\dfunchc: \opensetc^{\prime} \rightarrow \opensetc$ where $\opensetc, \opensetc^{\prime} \subseteq \dbasec$, \\
        $\dfuncpullc\dsectionc\restriction_{\opensetc}: \dsectionc \mapsto \dsectionc\restriction_{\opensetc} \circ \dfunchc$}

@@

\section{Construction}
\begin{frame}{How Do We Get From Data to Graphic?}
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/path_of_math.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Building an equivariant $\vartist$?}
    \begin{figure}
        \includegraphics[width=1\textwidth]{../paper/figures/path_of_q.png}
    \end{figure}
\end{frame}

\subsection{Measurement Specification $\vtotalc$}
\begin{frame}<presentation:1|handout:1>{Data to Measurable Components}
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/justnu.png}
    \end{figure}
\end{frame}

@@

\begin{frame}<presentation:0|handout:1>
    \frametitle{Transformations in Data $\vchannelc: \dsectionc \mapsto \vsectionc$}
    %rewrite in gamma notation
    \begin{figure}
        \includegraphics[.35\textwidth]{figures/math/nu_table.png}
    \end{figure}
    Given $\dsectionc(\dbasepointc) = \dsectionc(\dfunchc(\dbasepointc^{\prime}))$ and  $\vsectionc(\dbasepointc) = \vsectionc(\dfunchc(\dbasepointc^{\prime}))$
    \begin{description}
        \item[equivariance] $\dfunctc_{\vtotalc}(\vchannelc_{\opensetc}(\dsectionc))
        = \vchannelc_{\opensetc}(\dfunctc_{\dtotalc}(\dsectionc))$, $\vchannelc_{\opensetc} = {\vchannelc^{\prime}}_{\opensetc^{\prime}}$
        \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
    \end{description}
\end{frame}

@@

\subsection{Combining Components into Visualizations}
\begin{frame}<presentation:1|handout:1>{Components to Graphic}
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/math/justq.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Assembly $\vmarkc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
            \arrow[rrrr, "\vmarkc", color=artist] 
            \arrow[ddd, "\dfunctc_{\vtotalc} \circ \dfuncpullc_{\vtotalc}"', color=action] 
            \& \& \& \& 
            \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[ddd, "\dfunctc_{\gtotalc} \circ \dfuncpullc_{\gtotalc}", dotted, color=action]  \\
            \& 
            \opensetc 
             \&  \& 
            \opensetgc 
            \arrow[ll, "\vindexc"', color=functor]   \& \\
            \& 
            \opensetc^{\prime} 
            \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
            \&  \& 
            \opensetgc^{\prime} 
            \arrow[ll, "\vindexc"', color=functor] 
            \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
            \& \\
            \cgamma{\opensetc^{\prime}}{\vtotalc^{\prime}\restriction_{\opensetc^{\prime}}}
            \arrow[rrrr, "\vmarkc^{\prime}", color=artist] 
            \& \&  \& \& 
            \imartist{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
            \end{tikzcd}
        \end{equation*}
    \begin{alertblock}{equivariance}
       \begin{equation*}
        \vmarkc^{\prime}(\dfunctc_{\vtotalc}(\vsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vmarkc(\vsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
       \end{equation*}
    \end{alertblock}
\end{frame}

\begin{frame}{Combining Qs}
    \begin{columns}
    \column{.55\textwidth}       
    The codomain of all $\vmarkc$ targeting the same output space is the bundle $\gtotalc$ and $Hom(\gbasec_1, \gtotalc) + Hom(\gbasec_2, \gtotalc) = Hom(\gbasec_1 + \gbasec_2, \gtotalc)$; therefore 
    \begin{equation*}
        \bigsqcup_i \vmarkc_i(\cgamma{\opensetc_i}{\dtotalc_i\restriction_{\opensetc_i}}) = \cgamma{\mathop{\sqcup}_i\opensetgc_i}{\gtotalc\restriction_{\mathop{\sqcup}_i\opensetgc_i}})
    \end{equation*}
    when $\vindexc(\opensetgc_i) = \opensetc_i$

    \column{.45\textwidth}
    \begin{figure}
        \includegraphics[scale=.25]{figures/math/qcom.png}
    \end{figure}
    \end{columns}
\end{frame}

\begin{frame}{Compatible Qs}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&, column sep=small]
        \& 
        \cgamma{\opensetc}{\vtotalc^{a}\restriction_{\opensetc}} 
        \arrow[dd, "\vchannelc^{a\rightarrow b}", color=artist] 
        \arrow[rrd, "{\vmarkc_{\opensetc}}^{a}", color=artist] 
        \arrow[rrrrd, "\vmarkc^{a}", bend left, color=artist] 
        \&  \&  \& \&   \\
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[ru, "\vchannelc^a", color=artist] 
        \arrow[rd, "\vchannelc^b"', color=artist] 
        \& \&  \& 
        \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} 
        \&  \& 
        \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
        \arrow[ll, "\vindexpushc"', color=functor] \\
        \& \cgamma{\opensetc}{\vtotalc^{b}\restriction_{\opensetc}} 
        \arrow[rru, "{\vmarkc_{\opensetc}}^{b}"', color=artist] 
        \arrow[rrrru, "{\vmarkc}^{b}"', bend right, color=artist] 
         \&  \&  \&  \&  
    \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Implementation Choices: $\vartistc_{\dbasec} = \vartistc_{\gbasec}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, column sep=small]
            \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} 
            \arrow[rr, "\vchannelc_{\gbasec}", color=artist] 
            \arrow[rrrr, "\vartistc_{\gbasec}", bend left, color=artist]  
            \&  \& 
            \cgamma{\opensetgc}{\vindexpullc\vtotalc\restriction_{\opensetgc}} 
            \arrow[rr, "\vmarkc_{\gbasec}", color=artist] \&  \& 
            \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[dd, "\vindexpushc", color=functor] \\
             \&  \&   \&  \& \\
            \cgamma{\openset}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vchannelc_{\dbasec}", color=artist] 
            \arrow[rrrr, "\vartistc_{\dbasec}", bend right, color=artist] 
            \arrow[uu, "\vindexpullc", color=functor] \&  \& 
            \cgamma{\openset}{\vtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vmarkc_{\dbasec}", color=artist ] 
            \arrow[uu, "\vindexpullc", , color=functor] \&  \& 
            \imartist{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}}                 
            \end{tikzcd}
    \end{equation*}
\end{frame}
\end{document}
